Verifying Demonstrations

### 2017-08-01 properties.tex
Adds note about vote privacy, need of mix-nets
Removes question which is answered and a bit duplicate
Adds questions regarding blockchains

  \begin{question}
    How will this prevent us from reusing proofs from previous protests in 
    the same location(s)?
    What are the assumptions?
  \end{question}
  \begin{question}
    How hard is it to reuse old proofs?
    Forge all signatures due to changed values?
  \end{question}
\end{frame}

@@

  \begin{question}
    Malicious nodes want to provide Alice with a view that her proof is 
    included.
    Everyone else is provided a view without Alice.
    How can we ensure a consistent view for everyone?
    (Probably similar to the solution in Joakim's thesis.)
  \end{question}
\end{frame}

@@

  \begin{question}
    How to solve the Sybil problem?
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}
  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
  \end{question}
\end{frame}

@@

>>>>

  \begin{question}
    How hard is it to reuse old proofs?
    Forge all signatures due to changed values?
  \end{question}
\end{frame}

@@

  \begin{question}
    Malicious nodes want to provide Alice with a view that her proof is 
    included.
    Everyone else is provided a view without Alice.
    How can we ensure a consistent view for everyone?
    (Probably similar to the solution in Joakim's thesis.)
  \end{question}

  \begin{question}
    Under the protest conditions, we might have natural network splits.
    Is this a useful scenario?
  \end{question}

  \begin{question}
    How can we do blockchain branch and merge?
    That is needed to recover from the above attack.
  \end{question}
\end{frame}

@@

  \begin{question}
    How to solve the Sybil problem?
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}
  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
    Specifically ecash~\cite{ecash} and the like.
  \end{question}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
  \end{question}

  \begin{remark}
    Without anonymous submission we don't get vote pricacy, thus no receipt 
    freeness either.
  \end{remark}
\end{frame}
